---
title: "p8105_hw1_xl2851"
output: github_document
---
# problem 1

## 1.1 create a data frame
```{r}
library(tidyverse)

hw1_df = tibble(
  vec_numeric = rnorm(8),
  vec_logical = vec_numeric > 0,
  vec_char=c("a","b","c","d","e","f","g","h"),
  vec_factor=factor(c(0,1,2,0,1,2,0,1), levels=c(0,1,2), labels=c("low", "mediun", "high")))
```

## 1.2 take the mean of each variable
The mean of the vec_numeric is `r mean(pull(hw1_df, vec_numeric))`

The mean of the vec_logical is `r mean(pull(hw1_df, vec_logical))`

The mean of the vec_char is `r mean(pull(hw1_df, vec_char))`

The mean of the vec_factor is `r mean(pull(hw1_df, vec_factor))`

vec_numeric and vec_logical can take the mean. vec_char and vec_factor cannot take the mean.

## 1.3 convert
```{r results="hide",error=TRUE}
as.numeric(pull(hw1_df,vec_logical))
as.numeric(pull(hw1_df,vec_char))
as.numeric(pull(hw1_df,vec_factor))
```
Logical and factor vector can be converted into numeric vector while character vector cannot. This can explain why character vector can not take the mean.And this cannot explain why factor vector cannot take the mean.

## 1.4 second code crunk:convert and multiply
```{r echo=TRUE, results="hide",error=TRUE}
as.numeric(pull(hw1_df,vec_logical))*(pull(hw1_df, vec_numeric))
as.factor(pull(hw1_df,vec_logical))*(pull(hw1_df,vec_numeric))
as.numeric(as.factor(pull(hw1_df,vec_logical)))*(pull(hw1_df,vec_numeric))
```
# problem 2

## 2.1 create a data frame
```{r}
hw11_df=tibble(
  x=rnorm(500, mean=0, sd=1),
  y=rnorm(500, mean=0, sd=1),
  vec_logical_2=x+y>1,
  vec_numeric_2=as.numeric(vec_logical_2),
  vec_factor_2=as.factor(vec_logical_2),
)
```

## 2.2 description of the dataset 
The size of the dataset is `r nrow (hw11_df)` rows and `r ncol(hw11_df)` columns.

The mean of x is `r mean(pull(hw11_df, x))`

The median of x is `r median(pull(hw11_df,x))`

The standard deviation of the x is `r sd(pull(hw11_df,x))`

The proportion of cases for which x+y>1 is `r mean(pull(hw11_df,vec_logical_2))`

## 2.3 plots
### 2.3.1 plot of the logical variable(vec_logical_2)
```{r}
plot_logical=ggplot(hw11_df, aes(x=x, y=y, color=vec_logical_2))+ geom_point()
print(plot_logical + ggtitle("plot of the logical vector"))
ggsave("scatter_plot.pdf", height = 4, width = 6)
```
If "x+y>1" is true, the dots are in blue. If "x+y>1" is false, the dots are in red. 

### 2.3.2 plot of the numeric variable(vec_numeric_2)
```{r}
plot_numeric=ggplot(hw11_df, aes(x=x, y=y, color=vec_numeric_2))+ geom_point()
print(plot_numeric + ggtitle("plot of the numeric vector"))
```
When D=0, dots are in dark blue. When D=1, dots are in light blue.

### 2.3.3 plot of the factor variable(vec_factor_2)
```{r}
plot_factor=ggplot(hw11_df, aes(x=x, y=y, color=vec_factor_2))+ geom_point()
print(plot_factor + ggtitle("plot of the factor vector"))
```
If "x+y>1" is true, the dots are in blue. If "x+y>1" is false, the dots are in red. 